### 2013-09-18 structured_prediction/paper.tex
rest of hannes notes

\subsection{Factor Graphs and the Relation to Graphical Models}\seclabel{factor_graphs}
% one factor graph per instance? FIXME
In the case when $y$ is multivariate, a very general and widely used method to
specify the structure of a model, and therefore $\Phi$, is using \emph{factor
graphs}. A factor graph is a bipartite graph $(\mathcal{V}, \mathcal{F},
\mathcal{E})$, consisting of variable nodes $\mathcal{V}$, factor nodes
$\mathcal{F}$ and edges $\mathcal{E}$ connecting variables to factors. The
\emph{scope} $N_F$ of a factor $F \in \mathcal{F}$ is defined as
\begin{equation}
    N_F = \{ v \in \mathcal{V} \,|\, (v,F) \in \mathcal{E} \}
\end{equation}
The variable nodes of the factor graph correspond to the entries of the
variables $y$, that is $\mathcal{V} = \{1, \dotsc, n\}$, and each factor node
is associated with a \emph{factor} or \emph{potential function} $\psi_F$.
A factor graph represents a function\footnote{Traditionally factor graphs
 represent \emph{products} of factors.  To simplify presentation, we work
directly in the log-domain with respect to the more standard product representation.}
\begin{equation}\eqlabel{log_factor_graph}
    g(x, y) = \sum_{F \in \mathcal{F}} \psi_F(x, y_{N_F})
\end{equation}
Here, $y_{N_F}$ denotes the entries of $y$ indexed by $N_F$.

@@

This approach to structured prediction is closely related to 
approaches using \emph{probabilistic graphical models}.  Probabilistic graphical models are a
tool to express factorizations of probability distributions.  Similar to
\Eqref{log_factor_graph}, the joint probability distribution over a
multi-variate random variable $y$ can be expressed using a factor-graph:
\begin{equation}\eqlabel{graphicalmodel}
    p(y | x) = \frac{1}{Z_x}\prod_{F \in \mathcal{F}} \exp\left(\psi_F(x, y_{N_F})\right).
\end{equation}
Here
\begin{equation}
    Z_x = \sum_{y' \in \mathcal{Y}} \prod_{F \in \mathcal{F}} \exp\left(\psi(x, y'_{N_F})\right)
\end{equation}
is the normalization constant of the conditional distribution over $y$.
If $f$ is chosen as in \Eqref{linear_psi}, then the resulting distribution
belongs to the exponential family.

@@

The $1$-slack cutting plane method~\citep{joachims2009cutting} solves the
following reformulation of Equation~\Eqref{learning_equation}:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
Informally, the $1$-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points, and
then applying the $n$-slack algorithm with a single data point.
A detailed description can be found in Algorithm~\ref{alg_one_slack}.
%
By construction, only a single constraint is added in each iteration of
Algorithm~\ref{alg_one_slack}, leading to very small working sets $\W$.
This has the advantage of making the solution of the QP faster, as it contains far
less variables than in the $n$-slack algorithm. The down-side of this is that
the loss-augmented prediction problem has to be solved much more often until
convergence. This is reflected in a convergence rate of $O(\frac{1}{kT})$,
which scales with the inverse of the dataset size.

>>>>

\subsection{Factor Graphs and the Relation to Graphical Models}\seclabel{factor_graphs}
% one factor graph per instance? FIXME
In the case when $y$ is multivariate, a very general and widely used method to
specify the structure of a model, and therefore $\Phi$, is using \emph{factor
graphs}. A factor graph is a bipartite graph $(\mathcal{V}, \mathcal{F},
\mathcal{E})$, consisting of variable nodes $\mathcal{V}$, factor nodes
$\mathcal{F}$ and edges $\mathcal{E}$ connecting variables to factors. The
\emph{scope} $N_F$ of a factor $F \in \mathcal{F}$ is defined as
\begin{equation}
    N_F = \{ v \in \mathcal{V} \,|\, (v,F) \in \mathcal{E} \}
\end{equation}
The variable nodes of the factor graph correspond to the entries of the
variables $y$, that is $\mathcal{V} = \{1, \dotsc, n\}$, and each factor node
is associated with a \emph{factor} or \emph{potential function} $\psi_F$.
A factor graph represents a function\footnote{Traditionally factor graphs
 represent \emph{products} of factors.  To simplify presentation, we work
directly in the log-domain of the more standard product representation.}
\begin{equation}\eqlabel{log_factor_graph}
    g(x, y) = \sum_{F \in \mathcal{F}} \psi_F(x, y_{N_F})
\end{equation}
Here, $y_{N_F}$ denotes the entries of $y$ indexed by $N_F$.

@@

This approach to structured prediction is closely related to 
approaches using \emph{probabilistic graphical models}.  Probabilistic graphical models are a
tool to express factorizations of probability distributions.  Similar to
\Eqref{log_factor_graph}, the joint probability distribution over a
multi-variate random variable $y$ can be expressed using a factor-graph:
\begin{equation}\eqlabel{graphicalmodel}
    p(y | x) = \frac{1}{Z_x}\prod_{F \in \mathcal{F}} \exp\left(\psi_F(x, y_{N_F})\right).
\end{equation}
Here
\begin{equation}
    Z_x = \sum_{y' \in \mathcal{Y}} \prod_{F \in \mathcal{F}} \exp\left(\psi(x, y'_{N_F})\right)
\end{equation}
is the normalization constant of the conditional distribution over $y$.
If $f$ is chosen as in \Eqref{linear_psi}, then the resulting distribution
belongs to the exponential family, the class of probablility distributions most
commonly used in the graphical model iterature.

@@

The $1$-slack cutting plane method~\citep{joachims2009cutting} solves the
following reformulation of Equation~\Eqref{learning_equation}:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
Informally, the $1$-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points, and
then applying the $n$-slack algorithm with a single data point.
A detailed description can be found in Algorithm~\ref{alg_one_slack}.
%
By construction, only a single constraint is added in each iteration of
Algorithm~\ref{alg_one_slack}, leading to very small working sets $\W$.
This has the advantage of producing a QP that easyer to solve, as it contains far
less variables than in the $n$-slack algorithm. The down-side of this is that
the loss-augmented prediction problem has to be solved much more often until
convergence. This is reflected in a convergence rate of $O(\frac{1}{kT})$,
which scales with the inverse of the dataset size.
